---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(MASS)
data("women")
str(women)
```

```{r}
summary(women)
```
```{r}
ggplot(data = women, aes(x=weight, y=height))+geom_point()
```




```{r}
cor.test(women$weight,women$height)
```

```{r}
womenModel <- lm(height~weight,data= women) #predict height based on weight, using data women
```

```{r}
plot(womenModel)
summary(womenModel)
```

--> model : y= 25.723456+0.287249x



```{r}
ggplot(data= women, aes(x=weight, y=height))+geom_point()+geom_abline(mapping = aes(slope=womenModel$coefficients[2],intercept=womenModel$coefficients[1]),color='red')
```
```{r}
plot(womenModel,which =1)
```
```{r}

```

```{r}
layout(matrix(1:6,ncol=2,byrow = TRUE))
plot(womenModel,1:6)
```


- if we want the prediction result in an 95% interval:
```{r}
newWomen <- data.frame(weight=c(130,170))

predict(womenModel,newdata = newWomen,interval = "confidence")
```

a woman with the weight of 130 will have on avg a height ranging between 62.79 and 63.33
weight: 170, height ranging between 73.95 and 75.1
- if we want a concrete prediction result. cach1
```{r}
predict(womenModel,newdata = newWomen)
```

-cach 2 : if we want  
```{r}
predict(womenModel,newdata = newWomen,interval = "prediction")
```
--> this tells that 95% of the ppl with the weight of 130 have a height ranging between 62.07 and 64.05



### watch out: the data used for building model and the data used for prediction should have normal distribution

## check if the data follows the normal distribution with shapiro wilk test

```{r}
shapiro.test(women$weight)
shapiro.test(women$height)
```
--> if p<0.05 then the population is likely not a normal distribution and vice versa

#Exercise

```{r}
data("faithful")
summary(faithful)
```


```{r}
faithful
```


```{r}
faithfulModel <- lm(eruptions~waiting, data = faithful)
```
```{r}
ggplot(data= faithful, aes(x=eruptions, y=waiting))+geom_point()
```

```{r}
plot(faithfulModel)
summary(faithfulModel)
```


```{r}
predict(faithfulModel,newdata = data.frame(waiting=80))
```
--> with the waiting time 80, the eruption time is  to 4.17


#4 multiple linear regression using r


```{r}
data("mtcars")
?mtcars
View(mtcars)
```

```{r}
mpgModel <- lm(formula = mpg~cyl+disp+hp+drat+wt+qsec+vs+am+gear+carb,data = mtcars)
summary(mpgModel)
plot(mpgModel)
```

```{r}
mpgModel$fitted.values
```

#prediction with the model:

```{r}
mpgPredictions <- data.frame(mpg=mtcars$mpg,pred = mpgModel$fitted.values)
mpgPredictions
```

```{r}
ggplot(data = mpgPredictions,aes(x=mpg,y=pred))+geom_point()+geom_abline(mapping=aes(slope=1, intercept=0),color='red')
```

###stepwise regression
```{r}
reducedModel <- step(mpgModel,direction = "backward")
summary(reducedModel)
```




predictions with stepwise model:


```{r}
mpgPredictions_with_stepwisereg <-data.frame(mpg=mtcars$mpg,pred = reducedModel$fitted.values)

ggplot(data = mpgPredictions_with_stepwisereg,aes(x=mpg,y=pred))+geom_point()+geom_abline(mapping=aes(slope=1, intercept=0),color='red')

```

```{r}
mpgPredictions_with_stepwisereg
```




#exercise
predictions with only wt based-model (mpgModel2):

```{r}
mpgModel2 = lm(mpg~wt, data = mtcars)
summary(mpgModel2)
```

```{r}
mpg_with_wt <-data.frame(mpg=mtcars$mpg,wt= mtcars$wt)

ggplot(data = mpg_with_wt,aes(x=wt,y=mpg))+geom_point()+geom_abline(mapping=aes(slope=mpgModel2$coefficients[2], intercept=mpgModel2$coefficients[1]),color='red')
```





