---
title: "R Notebook"
output: html_notebook
---

#3 Data Frames


```{r}
medals <-data.frame(Country =c("NOR","GER","CHR"),
      Gold =c(16,12,9),
      Silver =c(8,10,4),
      Bronze =c(13,5,2))
medals
```


1.Select the first and third rows and the first and third columns:
select only col:
medals(c(1,3))
select only rows:
medals(c(1,3),)
```{r}
medals[c(1,3),c(1,3)]
```

2.Return a data frame that contains just the CHN row

```{r}
medals[3,]
```
3.Return a data frame that contains the medals of Norway and Germany
```{r}

medals[c(1,2),]


```

4.select countries who won ten or more gold medals and return the country and gold columns using the subset() function
```{r}
subset(medals,Gold>= 10 )
```

5.Sort the medals by bronze(descending)
```{r}
medals[order(medals$Bronze,decreasing = TRUE),]
```

changing  working directory : 
```{r}
getwd()
setwd("C:/Users/Saturn/Desktop/DATA_SCIENCE_UNI")
getwd()
```

#. Scaling up

```{r}
beijing2022 <- read.csv("Beijing2022.csv", sep = ";")

beijing2022
```





1. compute the total number of medals won for each country and add this as a fifth column to the dataframe

```{r}
Total <- rowSums(beijing2022[c(2,3,4)])
beijing2022 <- cbind(beijing2022,Total)
beijing2022

```


2.order the rows  by the total number of medals won in descending order
```{r}
beijing2022 <- beijing2022[order(beijing2022$Total,decreasing = TRUE),]
beijing2022
```

3.Sort the data first by the number of total medals won and then by the number of  gold medals won in descending order


```{r}
beijing2022 <- beijing2022[order(beijing2022$Total,beijing2022$Gold,decreasing = TRUE),]
beijing2022
```




4. Calculate the total number of cold, silver and bronze medals won at beijing 2022


```{r}
total_gold <- sum(beijing2022$Gold)
total_silver <- sum(beijing2022$Silver)
total_bronze<- sum(beijing2022$Bronze)


new_row <- data.frame(Country = "Total_medals",Gold = total_gold,Silver = total_silver, Bronze = total_bronze, Total=sum(beijing2022$Total) )
beijing2022<-rbind(beijing2022,new_row)


```

```{r}
beijing2022
```




5. the overall number of the medals won by all countries in the olypic games 2022 is 327



#4 Data exploration with R
MASS is package containing a lot of datasets
```{r}
install.packages("MASS")
```
```{r}
data("women")
women
```

```{r}
summary(women)
```



```{r}
hist(women$height)
```




```{r}
hist(x= women$height, breaks=4, main="Histogram showing women's heights",xlab= "Height")
```
mfrow =c(1,2) means we want to put 2 plots like in the following illustration
```{r}
par ( mfrow = c (1 ,2))
hist ( x = women $ height , breaks =4 , main = " Heights " , xlab = " Height " )
hist ( x = women $ weight , breaks =2 , main = " Weights " , xlab = " Weight " )
```
if we want our window just displaying one graph at a time:
```{r}
par(mfrow=c(1,1))

```

default scatterplot :
```{r}
plot(women)
```





