---
title: "R Notebook"
output: html_notebook
---
#3 Data visualisation 
##3.1 exploring time series data
```{r}
library(tidyverse)
library(lubridate)
```


```{r}
library(nycflights13)
```

```{r}

```

in tidyverse language : data frames are called tibbles
```{r}
flightsEdited <- flights%>%
mutate(date= make_date(year,month,day))
```
mutate() is used to create a new column with the result of make_date()
```{r}
flightsEdited 
```

```{r}
flightsEdited%>%
select(year,month,day,date)%>%
head
```
### we want to display the number of flights that depart NYC each day over time . Let'S group our data by date the count the occurences with the summarise()
```{r}
daily <-flightsEdited%>%
group_by(date)%>%
summarise(n=n())
head(daily)

```

###plot the flights
```{r}
ggplot(daily,aes(date,n))+geom_line()
```
###processing time serie data:
### add columns showing weekday and month for the date

```{r}
updateFlightsEdited <- flightsEdited%>%
mutate(weekday = wday(date,label = TRUE))%>%
mutate(month = month(date,label = TRUE))
updateFlightsEdited 
```

#exercise
```{r}
daily_january_flights <- updateFlightsEdited%>%
filter(month=="Jan")%>%group_by(date)%>%
summarise( n=n())

daily_january_flights 


```

```{r}
ggplot(daily_january_flights ,aes(date,n))+geom_line()
```
##flights to and from nyc (from or to jfk and lga) by month

```{r}
nyc_months_flights  <- updateFlightsEdited%>%
filter(origin %in%  c("JFK","LGA")| dest %in% c("JFK","LGA"))%>%
group_by(month)%>%
summarise(n=n())
nyc_months_flights

```
```{r}
ggplot(nyc_months_flights,aes( x=month,y=n))+ geom_point()
```
##flights to and from nyc (from or to jfk and lga) by weekday
```{r}
nyc_weekday_flights <- updateFlightsEdited%>%
filter(origin %in%  c("JFK","LGA")| dest %in% c("JFK","LGA"))%>%
group_by(weekday)%>%
summarise(n=n())
nyc_weekday_flights
```

```{r}
ggplot(nyc_weekday_flights,aes( x=weekday,y=n))+ geom_point()
```
#3.2 creating a correlation matrix
```{r}
data("mtcars")
str(mtcars)
```

### compute the correlatin for mtcars. all values must be numeric
```{r}
mcor <-cor(mtcars)
round(mcor,digits=2)
```
### visualization
```{r}
install.packages("corrplot")
```

```{r}
library(corrplot)
corrplot(mcor)
```


##visualize using ggcorr() from GGally package



```{r}
install.packages("GGally")
```

```{r}
library(GGally)
```

```{r}
ggcorr(mcor)
```
#exercise

```{r}
cor.test(mtcars$cyl,mtcars$disp)
```

#3.3 creating heatmap
```{r}
nba <- read.csv("http://datasets.flowingdata.com/ppg2008.csv",sep = ",")
head(nba)
```

##rename row index to be players'names
```{r}
row.names(nba)<- nba$Name

```
```{r}
head(nba)
```
##remove the name column
```{r}
nba <- nba[,2:20]
```

```{r}
nba
```
###heatmap() expects input as matrix but we have a dataframe so we have to convert df to matrix
```{r}
nbaMatrix <- data.matrix(nba
)
```
###plotting a heatmap
```{r}
heatmap(nbaMatrix,Rowv = NULL, Colv = NA,col = heat.colors(256),scale = "column",margins = c(5,10))
```
######## the darker the cell, the higher the value.




















