---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
```
```{r}
filter(mpg, manufacturer=="audi")
```





```{r}
filter(mpg,displ >2)
```

```{r}
filter(mpg, displ >2 & cyl>6)
```





```{r}
filter(mpg,manufacturer=="audi" ,year==1999)
```

```{r}
#filter(mpg,manufacturer=="audi" ,year==1999) would also return the same result
```
Exercise 

1. filter the row where the manufacter is audi or the year of production is 1999
```{r}
filter(mpg,manufacturer=="audi" |year==1999)
```


2. filter the row where the year of production is 1999 and the manufacturer is not audi

```{r}
filter(mpg,manufacturer!="audi" & year==1999)
```



```{r}
filter(mpg,(manufacturer=="audi"|manufacturer=="chevrolet") ,year==1999)%>%

count(manufacturer)
```



#filter(mpg,manufacturer %in% c("audi","chevrolet"),year==1999)




selecting sample

```{r}
sample_frac(mpg,0.05,replace = TRUE) #sample 5% of the data
```

```{r}
sample_n(mpg,10,replace = TRUE) #sample 10 rows the data
#hear replace = True means that one same row can be selected again
#everytime we run this function, the sample is renewed and gives different sample. If we want the consistent result , we use set.seed(x) where x is a nunmber before calling the same function
set.seed(3)
```


#3.2 Reordering rows- arrange()

```{r}
beijing2022Medals <- read.csv("Beijing2022.csv",sep=";")
```

```{r}
beijing2022Medals
```
#Exercise

1. 


```{r}
arrange(beijing2022Medals,desc(Gold),desc(Silver),desc(Bronze))

View(arrange(beijing2022Medals,desc(Gold),desc(Silver),desc(Bronze)))
```

#3.3 Selecting columns-select()
```{r}
library(dplyr)
```

```{r}
mpg
```

```{r}
select(mpg, manufacturer, hwy)
```

```{r}
select(mpg, starts_with("d"))
```

```{r}
select(mpg, manufacturer, hwy)%>%
filter(manufacturer!="chevrolet" & hwy >=20)
```

```{r}
select(mpg, manufacturer, hwy)%>%
filter(manufacturer!="chevrolet" & hwy >=20)%>%
arrange(desc(manufacturer))
```

these functions calls above are the same as 

```{r}
#mpg%>%select(manufacturer, hwy)%>%
#filter(manufacturer!="chevrolet" & hwy >=20)%>%
#arrange(desc(manufacturer))
```

#3.4 creating new variables -mutate()- this function allows creating a new variable based on the existing variables. Mutate() doesnt change the original data
e.g: create a new column/var for the total medals won using mutate():

```{r}
mutate(beijing2022Medals,Total = Gold+Silver+Bronze) #similar to rowSums


```



#3.5 Collapse many values down to a single summary - summarise()
this function allows us to summarise data into a single row of values 
```{r}
summarise(mpg,avg=mean(hwy))
```


```{r}
group_by(mpg,year,manufacturer)%>%
summarise(count=n())
```

```{r}
group_by(mpg,manufacturer)%>%
summarise(count=n())

#n() here stands for number . --> counting the number of rows for each manufacturer
```

#Exercise
1. how many unique models do each manufacturer produce?

```{r}
mpg
```

```{r}
group_by(mpg,manufacturer,model)%>%
summarise(count=n())
```
2. create a new column with a ratio of highway(hwy) cs city(cty) range called HwyCtyRatio

```{r}
Mpg_HwyCtyRatio<-mutate(mpg, HwyCtyRatio = hwy/cty)
Mpg_HwyCtyRatio
```


#4 combining datasets using R

```{r}
library(nycflights13)
library(tidyverse)
```


```{r}
nycflights13::airlines
```

```{r}
nycflights13::airports
```

```{r}
nycflights13::flights
```


```{r}
flight2 <- flights %>% select(year:day,hour,origin,dest, tailnum,carrier)

```



```{r}
flight2
```
joining the flight2 table with airlines table by carrier 

```{r}


flight2%>%
left_join(airlines,by="carrier")

```



































