---
title: "R_Assignment1"
output: html_notebook
---
# 3.1 Vector
1.create the following vector x=(1.2 2.3 0.2 1.1)



```{r}
x<- c(1.2,2.3,0.2,1.1)
```

2. check the class of the vector using the class() function

```{r}
class(x)
```

3.output the second element of the vector 
```{r}
x[2]
```

4.output the elements 2 and 3 of the vector

```{r}
x[c(2,3)]
```
5. replace the value of the first element of the vector
```{r}
x[c(-1)]
```

6.select all elements where the value is greater than 2

```{r}
x[c(2)]
```

7.One very helpful feature of vectors is that if we apply functions they will typically
be carried out on all of the vectors. Square each value of x and assign it to a new
variable called x.squared()

```{r}
x.squared <- x*x
```

8.. Append the value 5.2 to x.
```{r}
x+5.2
```


9. Compute the mean value of the updated vector x and check its length.
```{r}
mean(x+5.2)
length(x)

```

10. Create a named vector containing the number of days of each month. Further,
calculate the number of days in a year.


```{r}
days_each_month <-c(31,28,31,30,31,30,31,31,30,31,30,31)
names(days_each_month) <-c('jan','feb','march','april','may','june','july','august','sept','oct','nov','dec')

sum(days_each_month)

```


#3.2 Matrices


```{r}
P = matrix(
  c(2,4,3,1,5,7),
  nrow = 2,
  ncol = 3,
  byrow = TRUE
  )
```
1. Sum the values in the first row
```{r}
sum(P[1,])
```
2. sum the values in the first column

```{r}
sum(P[,1])
```
3.specify names for rows  (“Row1, Row”) and columns (“Col1”, “Col2”).


```{r}
dimnames(P)= list(
  
   c("row1","row2"),
   c("col1","col2","col3")
  
)
P

```
4.. Select the second row in the matrix p using its name (“Row2”).
```{r}
P['row2',]
```

5. Remove the third column from matrix p.
```{r}
P=P[,c("col1","col2")]
P
```

6. Add the column back again.
```{r}
P
```

```{r}
C=matrix(
  c(3,7),
  
  nrow = 2,
  ncol =1
 
  
)

cbind(P,C)

```


7.

```{r}
Bejing_Winter_Olympics =matrix(
  
  c(1,2,1,7,7,4,0,2,0,1,0,1,4,8,14,1,0,1,0,0,1,2,2,4,5,7,2,12,10,5,1,1,0,1,0,2,2,7,8,3,6,9,0,0,1,8,5,4,2,1,0,16,8,13,9,4,2,0,0,1,6,12,14,2,5,2,1,0,1,2,3,2,0,1,0,8,5,5,7,2,6,0,1,0,8,10,7),
  nrow=29,
  ncol=3,
  byrow= TRUE
)

dimnames(Bejing_Winter_Olympics)=list(
  c("Australia","Austria","Belasrus","Belgium","Canada","Czech Republic","Estonia","Finland","France","Germany","Great Britain","Hungary","Italy","Japan","Latvia","Netherlands","New Zealand","Norway","People's Republic of China","Poland","ROC","Republic of Korea","Slovakia","Slovenia","Spain","Sweden","Switzerland","Ukraine","United States of America"),
  c("Gold","Silver","Bronze")
)
Bejing_Winter_Olympics
```


# 3.3 Lists

list is one dimensional but each element can be a different type of variable. they can be number or character, vertor or matrix or tables of data . 

```{r}
a= list("a",1,c(4,5,6))
```
accessing element in list:
```{r}
a[[1]]
```
1.  Return the elements 1 and 3 as a list.
```{r}
a[c(1,3)]
```

2. Provide each element position a name (e.g., “One”, “Two”, “Three”).

```{r}
a= list("One" = "a","Two" = 1, "Three"= c(4,5,6))
a$One
a$Three
```































